SAT Solving for Vesicle Traffic Systems in Cells

### 2017-08-09 paper/bio_MTedit.tex
Review-update

\textbf{Molecular flows and steady state:} Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle. The total amount of each molecular type on each compartment can therefore increase or decrease. We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales. This implies incoming and outgoing fluxes are balanced for each molecular type at each compartment; this is the \textit{stability condition}.

@@

\textbf{Molecular regulation:} We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which a two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

>>>>

\textbf{Molecular flows and steady state:} Each edge is associated with a flux of all the molecular types carried by the corresponding vesicle. The total amount of each molecular type on each compartment can therefore increase or decrease. We assume the cell is in a steady state where each compartment’s composition does not vary over short time scales. Therefore, incoming and outgoing fluxes are balanced for each molecular type at each compartment; it is the \textit{stability condition}.

@@

\textbf{Molecular regulation:} We assume that for fusion to occur, the pair of SNARE types involved on the vesicle and compartment must both be in an active state. Whether these SNAREs are active or inactive depends on the other molecules found on the vesicle or compartment, respectively. We test many different versions of this kind of molecular regulation. Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}. This is motivated by the idea that pairing must generate an inactive bi-molecular complex.

### 2017-08-09 paper/related.tex
updated table2-description
Review-update

Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient}. GNR is a complex system driven by many complex rules. We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking}. Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge. In this paper, we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10). \\

>>>>

Recently model checkers found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}. GNR is a complex system driven by many complex rules. We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking,shukla}. Model checkers are far scalable in comparison to simulations, but scaling it to cases which are interesting biologically is still a challenge. In this paper, we have achieved the scalability required for analyzing vesicular transport network for eukaryotic cells, of total ten compartments (N = 10). \\
